---
title: "Anomaly Isolation"
output: html_notebook
---

# Local Density-Based outlier detection

We will explore the 2016 production data

```{r}
library(ensaiWind)
library(ldbod)
library(tidyr)
library(tidyverse)
library(lubridate)
```

```{r}
#-- define data path in the ensai library
data_path = file.path(system.file(package = "ensaiWind"), "extdata")

#-- load the 2016 production data
data_2016 = read.csv2(file.path(data_path, "wind-farm-1-signals-2016.csv"), header = T, dec = ".", sep = ";") %>%
  mutate(Timestamp = paste0(substr(Timestamp, 1, 10), " ", substr(Timestamp, 12, 19)),
         Datetime = as.POSIXct(Timestamp, "%Y-%m-%d %H:%M:%S"),
         Year_Month = format(Datetime, "%Y_%m"))

#-- load the 2016 failure data
failure2016 <- read.csv2(file.path(data_path, "htw-failures-2016.csv"), header = T, dec = ".", sep = ";") %>%
  mutate(Timestamp = paste0(substr(Timestamp, 1, 10), " ", substr(Timestamp, 12, 19)),
         Datetime = as.POSIXct(Timestamp, "%Y-%m-%d %H:%M:%S"))


```

```{r}
#-- group number of failures by turbine and by component
failure_turbine_component = failure2016 %>%
  group_by(Turbine_ID, Component) %>%
  summarize(total_failure_by_turb_comp = n()) %>%
  ungroup()

data.frame(failure_turbine_component)
failure2016
```

From an initial analysis, we can tell that the component that fails the most if the generator in turbine T06. It happened between June and November. We will isolate this turbine in this period and check for outliers using the local density based outlier detection
```{r}
head(data_2016[,c(1:4,84:85)])
```

```{r}
#-- Isolating turbine T06 between the months of June and November (06-11)
data_2016$Timestamp = ymd_hms(data_2016$Timestamp)
df_2016_T06 = filter(data_2016, Turbine_ID == "T06", 
                     Timestamp >= as.POSIXct("2016-06-01 12:00:00") & 
                       Timestamp <= as.POSIXct("2016-11-01 12:00:00"))

#-- plot one of the temperature variables
ggplot(df_2016_T06, aes(x=Timestamp, y = Gen_Bear_Temp_Avg)) + geom_line() + theme_bw()
```

```{r}
#-- applying the ldob function to compute outlier scores using neighborhood size of 50
scores = ldbod(df_2016_T06[,names(df_2016_T06)=="Gen_Bear_Temp_Avg"], k=50)

top2outliers = df_2016_T06[order(scores$lof,decreasing=TRUE)[1:20],names(df_2016_T06)=="Gen_Bear_Temp_Avg"]
top2outliers
t1 = df_2016_T06[which(df_2016_T06$Gen_Bear_Temp_Avg == max(top2outliers)),"Timestamp"]
t2 = df_2016_T06[which(df_2016_T06$Gen_Bear_Temp_Avg == min(top2outliers)),"Timestamp"]

f = failure2016 %>%
  filter(Turbine_ID == "T06") %>%
  select(Timestamp) %>%
  mutate(Timestamp = ymd_hms(Timestamp))

f


ggplot(df_2016_T06, aes(x=Timestamp, y = Gen_Bear_Temp_Avg)) + geom_line() + theme_bw() +
  annotate(geom="point", x=c(median(t2),median(t1)), y=unique(top2outliers), size=3, shape=21, fill="red") #+
  #geom_vline(xintercept = f, linetype="dotted", color = "blue", size=1.5)

```

The model identified two outliers for this specific model. Temperature = 205 and temperature = 22.

**SHOULD WE REPEAT THAT FOR ALL VARIABLES ??**

# Anomaly Detection

Using Twitter's anomaly detection package

```{r}
library(AnomalyDetection)
class(test$Datetime)
test = df_2016_T06[, c("Datetime", "Gen_Bear_Temp_Avg")]
test$Datetime = as.POSIXct(date(test$Datetime))

res = AnomalyDetectionTs(test, max_anoms=0.02, direction='both', plot=TRUE)
res$plot

data("raw_data")
head(raw_data)
```

