---
title: "Global View"
author: "Ensai/E-Lab"
date: "26/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
library(ensaiWind)
library(leaflet)
library(dplyr)
library(ggplot2)
library(viridis)
library(DT)
```

```{r 00, include = FALSE, message=FALSE, warning=FALSE, echo=FALSE}
data_path = file.path(system.file(package = "ensaiWind"), "extdata")
```

# Plant Layout

Please note that **wind-farm-1-locations.csv** represent the coordinates relatively to met mast location.  
It does not represent real geographical coordinates.

```{r load plant location, include = FALSE, message=FALSE, warning=FALSE, echo=FALSE}
plant <- read.csv2(file.path(data_path, "wind-farm-1-locations.csv"), header = T, dec = ".", sep = ";") %>%
  mutate(Name = gsub("Wind Turbine ", "WT", Item),
         Type = ifelse(Name == "Met Mast", "Met Mast", "Turbine")) %>%
  tidyr::separate(`Relative.Location`, c("Xcoord", "Ycoord"), sep = ",") %>%
  dplyr::select(Name, Type, Xcoord, Ycoord)
```

Just to have an idea of plant layout.  

```{r plant layout, include = TRUE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12}
ggplot(plant, aes(Xcoord, Ycoord, label = Name)) +
  geom_point(aes(colour = Type)) +
  labs(title = "Plant layout",
       caption = "Ensai/E-Lab",
       x = 'X coordinates (relative to met mast)',
       y = 'Y coordinates (relative to met mast)') +
  geom_text(aes(label=Name),hjust=0, vjust=0) + 
  theme(axis.text.x = element_text(size=6, angle=45))
  
```

# Data power curve

Table **Power_curve.csv**

```{r load data power curve, include = FALSE, message=FALSE, warning=FALSE, echo=FALSE}
pc <- read.csv2(file.path(data_path, "Power_curve.csv"), header = T, dec = ".", sep = ",") %>%
  rename(Ws = `Wind.speed..m.s.`,
         Power = `Power..kW.`)
```

After a quick look at that theorical power curve it seems that cut-in wind speed is 4m/s and cut-off is 25m/s.

```{r plot theorical power curve, include = TRUE, message=FALSE, warning=FALSE, echo=FALSE}
ggplot(pc, aes(x = Ws, y = Power)) +
  geom_point() +
  labs(title = "Theorical Power Curve",
       caption = "Ensai/E-Lab",
       x = 'Wind Speed (m/s)',
       y = 'Power (kW)')
```


# Data wind production {.tabset .tabset-pills}

## Data availability {.tabset .tabset-pills}

Data: **data_wind_prod.csv**

```{r load data wind prod, include = FALSE, message=FALSE, warning=FALSE, echo=FALSE}
prod <- read.csv2(file.path(data_path, "data_wind_prod.csv"), header = T, dec = ".", sep = ";") %>%
  mutate(Timestamp = paste0(substr(Timestamp, 1, 10), " ", substr(Timestamp, 12, 19)),
         Datetime = as.POSIXct(Timestamp, "%Y-%m-%d %H:%M:%S"),
         Year_Month = format(Datetime, "%Y_%m"))
```

**To do:** correct more precisely datetime

```{r get time range, include = FALSE, message=FALSE, warning=FALSE, echo=FALSE}
time_seq <- data.frame(dt_full = seq.POSIXt(min(prod$Datetime), max(prod$Datetime), by = "10 min"))


dt_full = seq.POSIXt(min(prod$Datetime), max(prod$Datetime), by = "10 min")
turbine = unique(prod$Turbine_ID)

prod_full = as.data.frame(expand.grid(dt_full, turbine)) %>%
  rename(dt_full = "Var1",
         Turbine = "Var2") %>%
  left_join(prod, by = c("dt_full" = "Datetime", "Turbine" = "Turbine_ID")) %>%
  mutate(Year_Month = format(dt_full, "%Y_%m"))
```

```{r compute na, include = FALSE, message=FALSE, warning=FALSE, echo=FALSE}
data_na = prod_full %>%
  dplyr::select(-c(dt_full, Timestamp)) %>%
  group_by(Turbine, Year_Month) %>%
  summarise_all(~sum(is.na(.))) %>%
  ungroup()

nb_Divisor <- as.symbol("nb_value")

data_comp = prod_full %>%
  group_by(Turbine, Year_Month) %>%
  summarize(nb_value = n()) %>%
  ungroup() %>%
  left_join(data_na, by = c("Turbine" = "Turbine", "Year_Month" = "Year_Month")) %>%
  mutate(across(-c(Turbine, Year_Month), ~ . / !! nb_Divisor)) %>%
  data.frame()

data_heatmap = data_comp %>%
  dplyr::select(-nb_value) %>%
  tidyr::gather(Feature, Na_pct, -c(Turbine, Year_Month))
```

### Turbine T01

```{r ws data availability T01, include=TRUE, message = FALSE, echo = FALSE, warning = FALSE, fig.width=14, fig.height=12}
heatmap_na("T01")
```

### Turbine T06

```{r ws data availability T06, include=TRUE, message = FALSE, echo = FALSE, warning = FALSE, fig.width=14, fig.height=12}
heatmap_na("T06")
```

### Turbine T07

```{r ws data availability T07, include=TRUE, message = FALSE, echo = FALSE, warning = FALSE, fig.width=14, fig.height=12}
heatmap_na("T07")
```

### Turbine T11

```{r ws data availability T11, include=TRUE, message = FALSE, echo = FALSE, warning = FALSE, fig.width=14, fig.height=12}
heatmap_na("T11")
```

## Classical relationships {.tabset .tabset-pills}


### Power curve: Power ~ Wind Speed

```{r plot obs power curve , include = TRUE, message=FALSE, warning=FALSE, echo=FALSE}
ggplot(prod, aes(x = Amb_WindSpeed_Avg, y = Prod_LatestAvg_ActPwrGen1)) +
  geom_point(aes(colour = `Turbine_ID`), alpha = 0.4) +
  labs(title = "Active Power Gen1 vs. Amb Wind Speed",
       caption = "Ensai/E-Lab",
       x = 'Wind Speed (m/s)',
       y = 'Power (kW)') + 
  guides(colour = guide_legend(override.aes = list(alpha = 1))) + 
  theme_minimal() +
  facet_wrap(~Year_Month)
```


**TO DO** plot the other relationships 

# Data failures {.tabset .tabset-pills}

```{r load data failure, include = FALSE, message=FALSE, warning=FALSE, echo=FALSE}
failure2016 <- read.csv2(file.path(data_path, "htw-failures-2016.csv"), header = T, dec = ".", sep = ";") %>%
  mutate(Timestamp = paste0(substr(Timestamp, 1, 10), " ", substr(Timestamp, 12, 19)),
         Datetime = as.POSIXct(Timestamp, "%Y-%m-%d %H:%M:%S"),
         Year_Month = format(Datetime, "%Y_%m")) %>%
  rename(Turbine_ID = `ï..Turbine_ID`)
failure2017 <- read.csv2(file.path(data_path, "htw-failures-2017.csv"), header = T, dec = ".", sep = ";") %>%
  mutate(Timestamp = paste0(substr(Timestamp, 1, 10), " ", substr(Timestamp, 12, 19)),
         Datetime = as.POSIXct(Timestamp, "%Y-%m-%d %H:%M:%S"),
         Year_Month = format(Datetime, "%Y_%m"))

failure = rbind(failure2016, failure2017)

```

## Number of failure by component

```{r failure by turbine and component, include = TRUE, message=FALSE, warning=FALSE, echo=FALSE}
failure_turbine_component = failure %>%
  group_by(Turbine_ID, Component) %>%
  summarize(total_failure_by_turb_comp = n()) %>%
  ungroup()

datatable(failure_turbine_component)
```
