---
title: "Wind Turbines Notebook"
author: "Guillaume Franchi"
output:
  html_notebook:
    number_sections: no
urlcolor: blue
---

# Importation of some packages used

```{r,echo=FALSE}
library(dplyr)
library(plyr)
library(plotly)
library(gridExtra)
library(stringr)
library(ensaiWind)
library(lubridate)
library(GGally)
```

# Data exploration

## Data Path

We specify the data path in the project :

```{r}
data_path = file.path(system.file(package = "ensaiWind"), "extdata")
```


## Importation of the data

We first select some data which might have been rearranged in the file `datatransfo.R`.
All the data (2016 and 2017) are gathered into the same data frame for the failures and met mast data.

We first import the failures.

```{r}
failures<-read.csv2(file.path(data_path,"total-failures.csv"),sep=";")
failures<- failures %>% arrange(Turbine_ID)
```

We import here the totality of the signals, for 2016 and 2017 :

```{r}
signals.2016<-read.csv(file.path(data_path,"wind-farm-1-signals-2016.csv"),sep=";")
signals.2016$Timestamp<-as.POSIXct(signals.2016$Timestamp,format="%Y-%m-%dT%H:%M:%S")
signals.2016$Turbine_ID<-as.factor(signals.2016$Turbine_ID)

signals.2017<-read.csv(file.path(data_path,"data_wind_prod.csv"),sep=";")
signals.2017$Timestamp<-as.POSIXct(signals.2017$Timestamp,format="%Y-%m-%dT%H:%M:%S")
signals.2017$Turbine_ID<-as.factor(signals.2017$Turbine_ID)
```

## Focus on the production

We will simply plot the data of production according to different variables for oth years 2016 and 2017. The function `plot.bymonth` that we created will simplify things.

### According to the windspeed

We select only the variables `Amb_WindSpeed_Avg` and `Prod_LatestAvg_TotActPwr`.

```{r}
plot.bymonth(signals.2016,"Amb_WindSpeed_Avg","Prod_LatestAvg_TotActPwr")
```

```{r}
plot.bymonth(signals.2017,"Amb_WindSpeed_Avg","Prod_LatestAvg_TotActPwr")
```


### According to the ambient temperature

We select only the variables `Amb_Temp_Avg` and `Prod_LatestAvg_TotActPwr`.

```{r}
plot.bymonth(signals.2016,"Amb_Temp_Avg","Prod_LatestAvg_TotActPwr")
```


```{r}
plot.bymonth(signals.2017,"Amb_Temp_Avg","Prod_LatestAvg_TotActPwr")
```

There is no visible effect here.

### According to the generator bearing temperature

We select the variables `Gen_Bear_Temp_Avg` and `Prod_LatestAvg_TotActPwr`.

```{r}
plot.bymonth(signals.2016,"Gen_Bear_Temp_Avg","Prod_LatestAvg_TotActPwr")
```

```{r}
plot.bymonth(signals.2017,"Gen_Bear_Temp_Avg","Prod_LatestAvg_TotActPwr")
```

## Focus on the Rotor Rpm

### According to the windspeed

We select only the variables `Amb_WindSpeed_Avg` and `Rtr_RPM_Avg`.

```{r}
plot.bymonth(signals.2016,"Amb_WindSpeed_Avg","Rtr_RPM_Avg")
```

```{r}
plot.bymonth(signals.2017,"Amb_WindSpeed_Avg","Rtr_RPM_Avg")
```


### According to the ambient temperature

We select only the variables `Amb_Temp_Avg` and `Rtr_RPM_Avg`.

```{r}
plot.bymonth(signals.2016,"Amb_Temp_Avg","Rtr_RPM_Avg")
```

```{r}
plot.bymonth(signals.2017,"Amb_Temp_Avg","Rtr_RPM_Avg")
```

No visible effect.

## Focus on the generator RPM

### According to the windspeed

We select only the variables `Amb_WindSpeed_Avg` and `Gen_RPM_Avg`.

```{r}
plot.bymonth(signals.2016,"Amb_WindSpeed_Avg","Gen_RPM_Avg")
```

```{r}
plot.bymonth(signals.2017,"Amb_WindSpeed_Avg","Gen_RPM_Avg")
```

### According to the ambient temperature

We select the variables `Amb_Temp_Avg` and `Gen_RPM_Avg`.

```{r}
plot.bymonth(signals.2016,"Amb_Temp_Avg","Gen_RPM_Avg")
```

```{r}
plot.bymonth(signals.2017,"Amb_Temp_Avg","Gen_RPM_Avg")
```


Still no visible effect for the ambient temperature.

## Correlation between variables

We want to find correlation between variables. In order to simplify the data, we will only select the average.

```{r}
df<-read.csv(file.path(data_path,"wind-farm-totalsignals.csv"),sep=";")
df.sel<- df %>% select(Gen_RPM_Avg,Gen_Phase1_Temp_Avg,Hyd_Oil_Temp_Avg,Gear_Oil_Temp_Avg,Gear_Bear_Temp_Avg,Nac_Temp_Avg,Rtr_RPM_Avg,Amb_WindSpeed_Avg,Amb_Temp_Avg,Prod_LatestAvg_TotActPwr,HVTrafo_Phase1_Temp_Avg,HVTrafo_Phase2_Temp_Avg,HVTrafo_Phase3_Temp_Avg,Cont_VCP_WtrTemp_Avg,Grd_Prod_Pwr_Avg,Gen_Bear2_Temp_Avg)

cor.mat<-cor(df.sel)
```

```{r}
cor.mat
```

```{r}
df<-read.csv(file.path(data_path,"wind-farm-1-signals-2016.csv"),sep = ";")
df<-df[which(month(df$Timestamp)==1),]
df.sel<- df %>% select(Gen_RPM_Avg,Gen_Phase1_Temp_Avg,Hyd_Oil_Temp_Avg,Gear_Oil_Temp_Avg,Gear_Bear_Temp_Avg,Nac_Temp_Avg,Rtr_RPM_Avg,Amb_WindSpeed_Avg,Amb_Temp_Avg,Prod_LatestAvg_TotActPwr,HVTrafo_Phase1_Temp_Avg,HVTrafo_Phase2_Temp_Avg,HVTrafo_Phase3_Temp_Avg,Cont_VCP_WtrTemp_Avg,Grd_Prod_Pwr_Avg,Gen_Bear2_Temp_Avg)
```

```{r,message=FALSE}
ggpairs(df.sel)
```


